\documentclass[11pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Packages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{pdflscape}
\usepackage{titlepic}
\usepackage{amsthm,amsmath,amssymb}
\usepackage{sansmathfonts}
\usepackage{listings}
\usepackage[shortlabels]{enumitem}
\usepackage{hyperref}
\usepackage{nameref}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{cite}
\usepackage[english]{babel} % English blindtext
\usepackage{blindtext} % macros for producing dummy output
\bibliographystyle{unsrt}
\usepackage{fancyvrb} % nicer verbatim handling
\usepackage{sansmathfonts}
\renewcommand{\familydefault}{\sfdefault}

\usepackage[colorinlistoftodos,textwidth=20mm,shadow]{todonotes}
% \usepackage[disable]{todonotes}
% \usepackage{draftwatermark}
% \SetWatermarkText{\parbox{\textwidth}{\centering DRAFT v0.1}}
% \SetWatermarkScale{1.0}
\usepackage{multicol}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Local defines
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\DeclareMathOperator{\sgn}{sgn}
\newcommand{\ith}{\ensuremath{i^\text{th}} }
\newcommand{\jth}{\ensuremath{j^\text{th}} }
\newcommand{\nth}{\ensuremath{n^\text{th}} }
\newcommand{\blditm}[1]{\item{\textbf{#1}}}

% Use \qst command for questions that need answering
\newcommand{\qst}[1]{\todo[color=magenta]{#1}}
% Use \lookup for items that need further research
\newcommand{\lookup}[1]{\todo[color=green]{#1}}
% Use \tsk for tasks that still need to be completed
\newcommand{\tsk}[1]{\todo[inline,color=cyan]{#1}}
% Use \idea for ideas not ready to be in text
\newcommand{\idea}[1]{\todo[inline,color=yellow]{#1}}
% Use \err to highlight were there are serious problems
\newcommand{\err}[1]{\todo[inline,color=red]{#1}}
% use to put a note in the margin
\newcommand{\sidenote}[2]{\todo[color=#1,size=\tiny]{#2}}

\newcommand{\etal}{\textit{et al. }}
\newcommand{\ie}[1]{\textit{i.e.} {#1}}
\newcommand{\eg}[1]{\textit{e.g.} {#1}}
\newcommand{\etc}[1]{\textit{etc.} {#1}}

% Use ``\cite{NEEDED}'' to get Wikipedia-style ``citation needed'' in document
\usepackage{ifthen}
\let\oldcite=\cite
\renewcommand\cite[1]{\ifthenelse{\equal{#1}{NEEDED}}{\textsuperscript{\texttt{\color{red}[citation~needed]}}\todo{citation needed}}{\oldcite{#1}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Preamble
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\author{Eric Wait}
\title{Future of Image Analysis Software}
\date{\today}

\begin{document}
	\maketitle
	\newpage

	\listoftodos
	\newpage

	\begin{multicols}{2}
	\section{Main Points}\label{sec:main_points}
		\begin{itemize}
			\item Data Storage
			\item Visualization \cite{Wait2014}
			\item Preprocessing \cite{Wait2019}
			\item Segmentation, Tracking, Connected Components \cite{Aaron2019}
			\item Summarization / High-level Analysis
			\item Validation / Correction \cite{Wait2014}
			\item Bulk Analysis
			\item Reporting \cite{NEEDED}
		\end{itemize}
	% \end{Main Points}

	\section{Data Storage}\label{sec:data_storage}
		Datasets are getting large and unwieldy.
		Modern pipelines are are complex and can be hindered by I/O.
		Data storage should emphasize the following:
		\begin{itemize}
			\item Lossless Compression \cite{Amat2015}
			\item Distributed / Parallel Access \cite{Amat2015}
			\item Fast Visualization \cite{Wait2014}
			\item Fast Preprocessing \cite{Wait2019}
			\item Operating System Integration
			\item[\vspace{\fill}]
		\end{itemize}
	% \end{Data Storage}
	
	\section{Visualization}\label{sec:visualization}
		Visualization is often done on a case by case manner or for a specific need \cite{NEEDED}.
		The method of visualization can hinder insight.
		There are many visualization techniques written for individual niches \cite{NEEDED}.
		Modern visualization needs to be:
		\begin{itemize}
			\item Fast
			\item Intuitive
			\item Informative
			\item Customizable
			\item High Quality
			\item Physically Based
			\item Easy to make figures and movies
			\item Reproducible
			\item Reporting
			\item[\vspace{\fill}]
		\end{itemize}
	% \end{Visualization}

	\section{Preprocessing}\label{sec:preprocessing}
		Most data needs some preprocessing to remove background or clean up unwanted signal \cite{Aaron2019}.
		There are a variety of new methods that are yet to be implemented in general software \cite{NEEDED}.
		Preprocessing can be time consuming on large datasets.
		\tsk{Hydra graph here?}
		Many filters have not been efficiently implemented for 3-D or distributed architecture (GPU, local cluster, cloud computing, \etc).
		Edge artifacts are an increasing issue with anisotropic data (\eg{confocal}).
	% \end{Preprocessing}\label{sec:preprocessing}

	\section{Segmentation, Tracking, Connected Component Analysis}\label{sec:seg_track_cc_analysis}
	% \end{Segmentation, Tracking, Connected Component Analysis}\label{sec:seg_track_cc_analysis}
	
	\section{Summarization / High-level Analysis}\label{sec:sum_highlevel_analysis}
	% \end{Summarization / High-level Analysis}\label{sec:sum_highlevel_analysis}
	
	\section{Validation / Correction}\label{sec:validation_correction}
	% \end{Validation / Correction}\label{sec:validation_correction}
	
	\section{Bulk Analysis}\label{sec:bulk_analysis}
	% \end{Bulk Analysis}\label{sec:bulk_analysis}
	
	\section{Reporting}\label{sec:reporting}
		Filters should be well documented to include the references that first introduced the technique.
		Processing pipeline should produce a report that includes references, order, and parameters.

	% \end{Reporting}\label{sec:reporting}

	\end{multicols}

	\newpage
	\bibliography{ref}
\end{document}
